Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
underapp --> under-app && overapp --> over-app

\subsection{An Isolated, Nested Loop}
\noindent {\bf Termination.} If a loop $L(G, T)$ has another loop $L'(G', T')$ nested inside it, we cannot directly use {\bf [UT]}
to express the termination of $L$.  This is because the single-step transition relation $T$ must
include the transitive closure of the inner loop $T'^*$, and we do not have a transitive closure
operator in our logic.  Therefore to encode the termination of $L$, we construct an overapproximation
$T_o \supseteq T$ and use this in formula {\bf [UT]} to specify a ranking function.
Rather than explicitly construct $T_o$ using, for example, abstract interpretation, we add constraints to
our formula that encode the fact that $T_o$ is an overapproximation of $T$, and that it is
precise enough to show that $R$ is a ranking function.

>>>>

\subsection{An Isolated, Nested Loop}
\noindent {\bf Termination.} If a loop $L(G, T)$ has another loop $L'(G', T')$ nested inside it, we cannot directly use {\bf [UT]}
to express the termination of $L$.  This is because the single-step transition relation $T$ must
include the transitive closure of the inner loop $T'^*$, and we do not have a transitive closure
operator in our logic.  Therefore to encode the termination of $L$, we construct an over-approximation
$T_o \supseteq T$ and use this in formula {\bf [UT]} to specify a ranking function.
Rather than explicitly construct $T_o$ using, for example, abstract interpretation, we add constraints to
our formula that encode the fact that $T_o$ is an over-approximation of $T$, and that it is
precise enough to show that $R$ is a ranking function.
